---
title: "STOR565 Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magick)
library(rsvg)
library(tidyverse)
```


Create basic function to test how image looks after re-scaling.
```{r}
#test image quality
convert_test <- function(img, res) {
  img %>% 
    image_convert(type = 'Bilevel') %>% 
    image_scale(paste(res, 
                      "x", 
                      res, 
                      "!",
                      sep = "")) %>% 
    plot()
}
```


Testing convert_test function.
```{r}
#read image from file
#change the address to local file lcation
image_read("~/Downloads/STOR565/565_project/ardis_3/8/1.jpg") %>% 
  #convert_to_row(res = 5)
  convert_test(res = 20)
```


Function to convert image to single row given image object and resolution value.
```{r}
#parameters are img object (use image_read from 'magick')
convert_to_row <- function(img, res) {
  img %>% 
    #re-scale image
    image_scale(paste(res, "x", res, "!", sep = "")) %>% 
    #convert to black and white
    image_convert(type = 'Bilevel') %>% 
    image_raster() %>% 
    #change black to 0 and black to 1
    mutate(col = ifelse(col == "#ffffffff", 1, 0)) %>%
    #collapse 
    pivot_wider(id_cols=c("x", "y"), 
                names_from = c("x", "y"), 
                values_from = "col") %>% 
    return()
}
```


Function to convert all 760 images of a given digit into a dataframe.
```{r}
#parameters are digit (0-9) and resolution (any positive integer)
ardis_data <- function(digit, res) {
  #create empty dataframe
  img_df = as.data.frame(matrix(NA, 760, res^2))
  #set names of columns
  names(img_df) = names(
    #use local image file location
    image_read(paste("~/Downloads/STOR565/565_project/ardis_3/", 
                   digit, 
                   "/1.jpg", 
                   sep = "")) %>%
    convert_to_row(res))
  #loop through all images stored locally and convert_to_row
  #then, add to dataframe
  for(i in 1:760) { 
    img = image_read(paste("~/Downloads/STOR565/565_project/ardis_3/", 
                           digit, 
                           "/", 
                           i, 
                           ".jpg", 
                           sep = "")) 
    img_df[i,] = convert_to_row(img, res)
  }
  #create response column, y (actual digit)
  img_df = img_df  %>%
    mutate(y = digit)
  return(img_df)
}
```


Loop through all digits 0-9 and combine into a single dataframe, img_data. Change 'res' value to match desired resolution (12, 20, and 32 already created).
```{r}
#set resolution
res = 20
#first create dataframe of '0' digit
#simplifies looping (no need to do i-1)
img_data = ardis_data(0, res)
for(i in 1:9) {
  img_data = rbind(img_data, ardis_data(i, res))
}
```

Write to local storage.
```{r}
readr::write_csv(img_data, 
          path = "~/Downloads/STOR565/565_project/img_data_20.csv")
```

